A performance assessment of evolutionary algorithms in a volunteer computing system

### 2016-03-14 PPSN2016/paper.Rnw
Conclusions

Our main intention in this paper was to focus on the algorithm itself
so that it became as effective as possible, and able to use
computation by volunteers in the best possible way, or at least better
than the initial configuration. This initial configuration included
{\em overlaps} or clients running islands that had actually started in
a previous experiment in the set. If we are interested in measuring
how many users or their behavior in bulk this is not so important, but
in this case our focus was on the algorithm so we had to try that all
clients participating in it started more or less at the same time and
from a random population. In fact, we managed to do so, except in some
byzantine cases, by making the clients restart when the cache size
collapses to 1 or to a size much smaller than the current; we called
this client configuration {\tt reboot} and {\tt cachecrash}.  This
configuration achiever a positive secondary effect: all clients
contribute to fill the cache, having thus an actual effect on the
chromosome pool and effectively making all clients present contribute
to the simulation.

@@

This future holds many challenges which once again will go in two
different directions: gathering more users and improving the
efficiency of the algorithm run in an asynchronous way by the
users. In the first case, it will be interesting to make it more {\em
  social} by comparing local performance to other's contributions, and
showing it in a graph or being able to tweet advances or the fact that
the solution has been found. Anything that keeps the users running the
system and attracts new users will contribute to the speed of finding
the solution. And the algorithm will have to be improved, mainly by
making the population more diverse. Right now there is a rigid policy
of contribution to the pool: send the best individual, but this could
be relaxed. Some other policies could also be tested, as well as
running heterogenous algorithms in the same way that was done in
\cite{DBLP:journals/grid/ValdezTGVO15}. Diversity, as in any other
evolutionary algorith, seems to be the key, but there are many ways of
approaching it.

>>>>

Our main intention in this paper was to focus on the algorithm itself
so that it could became as effective as possible, and would be able to use
computations by volunteers in the best possible way, or at least better
than the initial configuration. This initial configuration included
{\em overlaps} or clients running islands that had actually started in
a previous experiment in the set. If we are interested in measuring
how many users or their behavior in bulk this is not so important, but
in this case our focus was on the algorithm so we had to try that all
clients participating in it started more or less at the same time and
from a random population. In fact, we managed to do so, except in some
byzantine cases, by making the clients restart when the cache size
collapses to 1 or to a size much smaller than the current; we called
this client configuration {\tt reboot} and {\tt cachecrash}.  This
configuration achiever a positive secondary effect: all clients
contribute to fill the cache, having thus an actual effect on the
chromosome pool and effectively making all clients present contribute
to the simulation.

@@

This future work holds many challenges which once again will go in two
different directions: gathering more users and improving the
efficiency of the algorithm run in an asynchronous way by the
users. In the first case, it will be interesting to make it more {\em
  social} by comparing local performance to other's contributions, and
showing it in a graph or being able to tweet advances or the fact that
the solution has been found. Anything that keeps the users running the
system and attracts new users will contribute to the speed of finding
the solution. And the algorithm will have to be improved, mainly by
making the population more diverse. Right now there is a rigid policy
of contribution to the pool: send the best individual, but this could
be relaxed. Some other policies could also be tested, as well as
running heterogenous algorithms in the same way that was done in
\cite{DBLP:journals/grid/ValdezTGVO15}. Diversity, as in any other
evolutionary algorith, seems to be the key, but there are many ways of
approaching it.
